Summary of Late Winter2013 Production: ip\_diffim

### 2013-03-15 W13report.tex
More text summarizing the process.  ACB

For each source returned by DiaCatalogSourceSelector, we create a {\tt
  KernelCandidate} instance, which holds substamps of $T(x,y)$ and
$S(x,y)$ centered on the source.  These will be used to fit for a
local solution to $K(u,v)$; the ensemble of local solutions at each
source's $x,y$ will be used to fit for the full spatial solution
$K(u,v,x,y)$.  We emphasize that the dimensions of the substamps is
important.  Note from equation~\ref{eq-soln} that the coefficients
$a_i$ are derived from a convolution of the template substamp with the
kernel basis functions $K_i$.  This convolution means that
kernelSize//2 pixels along each substamp edge are rendered unusable.
To maintain a siginificant number of pixels in $C_i$, we set the
KernelCandidate dimensions to be twice that of the kernel (i.e. the
number of pixels remaining in $C_i$ is equal to the number of pixels
in the kernel, which is fewer than the number of bases $i$).

>>>>

For each source $j$ returned by DiaCatalogSourceSelector, we create a
{\tt KernelCandidate} instance, which holds substamps of $T_j(x,y)$
and $S_j(x,y)$ centered on the source.  These will be used to fit for
a local solution $K(u,v)$; the ensemble of local solutions at each
source's $x,y$ will be used to fit for the full spatial solution
$K(u,v,x,y)$.  We emphasize that the dimensions of the substamps is
important.  Note from equation~\ref{eq-soln} that the coefficients
$a_i$ are derived from a convolution of the template substamp with the
kernel basis functions $K_i$.  This convolution means that
kernelSize//2 pixels along each substamp edge are rendered unusable.
To maintain a siginificant number of pixels in $C_i$, we set the
KernelCandidate dimensions to be twice that of the kernel (i.e. the
number of pixels remaining in $C_i$ is equal to the number of pixels
in the kernel, which is fewer than the number of bases $i$).  For each
KernelCandidate, we solve for $K(u,v)$ and create a local difference
image $D_j(x,y)$.  We evaluate several statistics on this local
difference image, normalized by the square root of its variance, which
puts the pixels in units of sigma.  We measure the mean sigma, the RMS
of this distrubion, the $\chi^2$ of these pixels normalized by the
degrees of freedom (number of pixels in $D(x,y)_j$ minus the number of
kernel bases), and the mean squared error.  These are referred to as
the LOCAL kernel metrics, and reflect how appropriate the chosen
kernel basis is.

The ensemble of {\tt KernelCandidates} is then used to constrain a
spatial model of the kernel $K(u,v,x,y)$.  This is done using the {\tt
  SpatialCellSet} formalism, whereby the {\tt KernelCandidates} are
distributed across the image in a grid of {\tt SpatialCells}.  At most
3 {\tt KernelCandidates} per {\tt SpatialCell} are input to a spatial
model of the kernel.  This formalism attempts to distribute
constraints on the spatial model evenly across the image.  For the
spatial kenrel model, we assume that each of the kernel coefficients
$a_i$ may be represented by a $N^{th}$ order 2--dimensional Chebyshev.
Normally, we would perform sigma--clipping iterations on candidates
having bad residuals after spatial modelling.  However in this
production we expect that all objects should fit, so we perform no
sigma clipping.  Having generated the full spatial solution
$K(u,v,x,y) = \sum_i a_i(x,y) K_i(u,v)$, we evaluate the solution at
the position of each {\tt KernelCandidate} and generate the metrics
defined above.  These are referred to as the SPATIAL kernel metrics.
Importantly, we interpolate this solution to the positions of the
control sample, which were explicitly {\it not} used in the spatial
fit, and evaluate these same metrics.  The differences between the
{\tt KernelCandidate} LOCAL and SPATIAL metrics, as well as the values
of the SPATIAL metrics for the control sample, reflect the
appropriateness of the spatial model and our ability to interpolate
and extrapolate to the full extent of the images.
